### 2022-07-25 main/chapter_2ljets.tex
explain why zero low

These three estimates are labelled `MC', `MM', `Mean', and we combine them into
the `Max' estimate.
Each is described here.
\begin{itemize}
\item The `MC' estimate takes the simulated estimate that was previously reported
in Table~\ref{tab:2ljets_fnp_negative_mm}.
\item The `MM' estimate modifies the Matrix Method result,
also from Table~\ref{tab:2ljets_fnp_negative_mm}, by shifting its central
value to a small positive value chosen baselessly as $0.01$ and by adding
its statistical and systematic uncertainties linearly
(not in quadrature to conservatively cover a correlated variation)
to assign a high variation.
\end{itemize}
After I had proposed a combination of these two estimates, reviewers
suggested additionally using the statistical properties of samples in looser
selections.
This became the third `Mean' estimate.
\begin{itemize}
\item The `Mean' follows an idea that the smallest assignable value should
be comparable to typical Matrix Method weights, and those typical values
are extracted from a region requiring pre-selection,
from Table~\ref{tab:2ljets_presel},
$\mll \in 71\textrm{--}101$,
$\mjj \in 60\textrm{--}100$,
$\njet \geq 2$, and
$\nbtag \leq 1$.
Its central value takes the mean weight of Matrix Method samples in this
selection, which is $\mu^\textrm{M} = 0.0202$.
Statistical errors are set to the root of the mean squared weight,
which is $\sigma^\textrm{M}_\textrm{stat} = 0.1132$,
and systematic errors are set as the larger absolute deviation on the mean
from the up and down variations in the Matrix Method weights, which comes out
$\sigma^\textrm{M}_\textrm{sys} = 0.0226$.
Finally, the `Mean' high variation is their linear sum;
$\mu^\textrm{M} + \sigma^\textrm{M}_\textrm{stat} +
\sigma^\textrm{M}_\textrm{sys} = 0.1560$.
\end{itemize}
All low variations are set to zero.

>>>>

These three estimates are labelled `MC', `MM', `Mean', and we combine them into
the `Max' estimate.
Each is described here.
\begin{itemize}
\item The `MC' estimate takes the simulated estimate that was previously reported
in Table~\ref{tab:2ljets_fnp_negative_mm}.
\item The `MM' estimate modifies the Matrix Method result,
also from Table~\ref{tab:2ljets_fnp_negative_mm}, by shifting its central
value to a small positive value chosen baselessly as $0.01$ and by adding
its statistical and systematic uncertainties linearly
(not in quadrature to conservatively cover a correlated variation)
to assign a high variation.
\end{itemize}
After I had proposed a combination of these two estimates, reviewers
suggested additionally using the statistical properties of samples in looser
selections.
This became the third `Mean' estimate.
\begin{itemize}
\item The `Mean' follows an idea that the smallest assignable value should
be comparable to typical Matrix Method weights, and those typical values
are extracted from a region requiring pre-selection,
from Table~\ref{tab:2ljets_presel},
$\mll \in 71\textrm{--}101$,
$\mjj \in 60\textrm{--}100$,
$\njet \geq 2$, and
$\nbtag \leq 1$.
Its central value takes the mean weight of Matrix Method samples in this
selection, which is $\mu^\textrm{M} = 0.0202$.
Statistical errors are set to the root of the mean squared weight,
which is $\sigma^\textrm{M}_\textrm{stat} = 0.1132$,
and systematic errors are set as the larger absolute deviation on the mean
from the up and down variations in the Matrix Method weights, which comes out
$\sigma^\textrm{M}_\textrm{sys} = 0.0226$.
Finally, the `Mean' high variation is their linear sum;
$\mu^\textrm{M} + \sigma^\textrm{M}_\textrm{stat} +
\sigma^\textrm{M}_\textrm{sys} = 0.1560$.
\end{itemize}
All low variations are set to zero for these replacement FNP estimates, to
encode that the yield is compatible with zero, but more importantly to give
a slow extrapolation on the low side (from the small central value to zero)
and reduce the risk from non-physical negative yields in the HistFactory model.
